### 2008-09-18 doc/client/client_technical.tex
JobDescription details

>>>>

The parsing is possible from any language but by the other hand the
output generation is not so widespread supported. There is only the
JSDL and JDL output generation implemented yet and there are limitations
too.

The conversion means mainly a syntactial transformation and of course
can do nothing in that cases where is not enough data to assemble the
given attribute or can loose information where the received attribute
has no equivalent pair in the output language.

By the JSDL output generation the {\JobDescription} class is using the
core JSDL's capabilities raised with the JSDL-POSIX and JSDL-ARC extensions.
The loss of information is minimal in case of generating such an output.

By the JDL generation the last version of JDL specification was used 
(v0.9\footnote{\url{https://edms.cern.ch/file/590869/1/EGEE-JRA1-TEC-590869-JDL-Attributes-v0-9.pdf}})
and only the not lapsing attributes are implemented (the deprecated
attributes are excluded).

Actually there is no XRSL generation implemented yet.
